Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
Shorter crisp section 2 with ammended notations

Let us straighten the notations next. 
We should have 
\begin{itemize}
\item 
$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties 
\item 
$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients 
(in particular, are the orders $M_G, N_G$ the same? 
\item 
we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
$$
\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
$$ 
where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
\item 
finally, we encompass the errors resulting from employing finite parameters representation, 
which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
$$
\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
$$ 
Dario, can you write it out explicitly? In other words, if 
$$
\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
$$ 
then what is the explicit expression of 
$$
\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
$$
(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
\item 
Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
This controller's transfer function will be subject to the same quantisation and precision limits as the plant's: 
we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
\item[]
\item 
An additional source of error can be related to the fact that a plant transfer function, 
per se a physical entity, is actually represented in a program imprecisely: 
this would mean that $G(s)$ is actually 
$$
G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
$$ 
which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
We should argue that this error is encompassed by the one derived above (or isn't it?). 
\end{itemize}
}

@@

\red{[This section and the next should be merged into a crisp section with the background on DSVerifier, if not included in previous work? 
Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}

@@

Since $G(z)$ is an approximation of $G(s)$ calculated via a discrete z transform using a selected sampling time, we denote the error in the approximation as $\Delta{G}_P$
\begin{align}
\small
\label{parametric_plant_tf}
\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
&=G(z,T)+\Delta{G}_P(z,T).
\end{align}
Note that $\Delta{G}_P$ is undefined and upperbound by a user defined percentage which relates to the nature of the z transform and the sampling time. For simplicity we will use $G(z)$ to represent $G(z,T)$.

Let $\tilde C(z)$ and $\tilde G(z)$ be the same transfer functions represented using a Fixed Point Finite Word Length with integer size $I$ and fractional size $F$. We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ domain, 
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
However, since the plant was originally in the real domain,
\begin{align}
\small
\label{digital_plant_tf}
&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \nonumber \\
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
\end{align}

\vspace{1 mm} 
\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by the rounding off effect. We may encompass all the uncertainty as $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$. Since this value is nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is denoted by $\mathfrak{G}$.

@@

\red{[The following description can be made shorter, crisper?]}

The DSVerifier verification flow is illustrated in
Fig.~\ref{DSVerifier_process}.  Steps $1$ to $5$ are performed by users and
Steps A to D are automatically performed by DSVerifier, which accepts the
digital controller transfer functions together with the plant model.  For
any digital controller, implementation details should be provided ({\it
e.g.}, number of bits, realization, and sample time).

@@

In Step $1$, the user provides inputs $g_0$ and $\Delta{g}\%$ ({\it i.e.},
percentage form of $\Delta{g}$), which contain the plant model and the
interval, respectively.  In Step $2$, a digital controller must be designed
with any preferred method, where $c_0$ is obtained.  The controller
numerical representation and realization form are chosen in Steps $3$ and
$4$, respectively.  In Step $5$, the user finally configures the
verification parameters ({\it e.g.}, verification time, properties, and BMC
tool).  After that, DSVerifier verification engine performs an (automatic)
verification of the desired property $\phi$ ({\it i.e.}, stability).  The
user steps described in Steps $1$--$5$ result in an ANSI-C code that should
be used as an input for DSVerifier.

In Step A, DSVerifier constructs a non-deterministic model to represent the
plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
Step B using implementation details provided from Steps $2$ and $3$, and
then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
intermediate ANSI-C code for the digital system implementation, which is
used as input for the model-checker, as pointed in Step D.

This intermediate ANSI-C code model has three main modules: digital
controller code to be embedded into the microprocessor; plant model code,
which simulates the plant model dynamics considering uncertainties; and
``assert'' and ``assume'' statements, which control the verification flow. 
For the digital controller code, transfer functions coefficients are
quantized and deterministic, and all operations use fixed-point arithmetic. 
\textcolor{red}{In the plant model code, transfer function coefficients are
not quantized, but represented with maximum precision based on float
data-type variables}; they are treated as non-deterministic variables to
support model uncertainties.  The directive ``assume'' bounds
non-deterministic variables, {\it i.e.}, inputs and plant uncertain
coefficients.

Finally in the Step D, the translation of ANSI-C code into SAT/SMT formulae
is done by a back-end model-checking tool ({\it e.g.},
CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).  Here, DSVerifier
symbolically checks a given property $\phi$ with respect to closed-loop
systems, which are composed by $FWL[c_0]$ and every $g$ in $\mathfrak{G}$. 
If any property violation is found, then DSVerifier reports a
counterexample, which contains system inputs or parametric deviations
$\Delta{g}\%$ that lead the system to a failure.  A successful verification
result is reported if the system is safe with respect to $\phi$.  In
particular, the stability verification is complete and sound, since it does
not depend on system outputs and inputs.

@@

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
    \node[draw=none] (r) {r};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (u) at ([xshift=1cm,yshift=.1cm]cz)  {u};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu2$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(s)}};
   \& \coordinate (aux1);
   \& \node[draw=none] (y) {y};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $u_d(k)$ at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$. \red{[Right: so under this assumption, we really only focus on the quantisation effects introduced by the ADC, correct? Let us not mix up the role and the influence of the two blocks.]}
%
\end{myassumption}

@@

For convenience, we will use only the notation $G(z)$ for represent the pulse transfer function.
\end{mylemma}
%\red{[Here the dependence on the sampling time T needs to appear somewhere.]} 
%\green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
%\red{[ok, then let's call it $G(z,T)$ as I suggested earlier.]}

>>>>

%Let us straighten the notations next. 
%We should have 
%\begin{itemize}
%\item 
%$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties 
%\item 
%$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients 
%(in particular, are the orders $M_G, N_G$ the same? 
%\item 
%we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
%$$
%\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
%$$ 
%where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
%\item 
%finally, we encompass the errors resulting from employing finite parameters representation, 
%which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
%$$
%\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
%$$ 
%Dario, can you write it out explicitly? In other words, if 
%$$
%\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
%$$ 
%then what is the explicit expression of 
%$$
%\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
%$$
%(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
%\item 
%Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
%This controller's transfer function will be subject to the same quantisation and precision limits as the plant's: 
%we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
%\item[]
%\item 
%An additional source of error can be related to the fact that a plant transfer function, 
%per se a physical entity, is actually represented in a program imprecisely: 
%this would mean that $G(s)$ is actually 
%$$
%G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
%$$ 
%which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
%We should argue that this error is encompassed by the one derived above (or isn't it?). 
%\end{itemize}
}

@@

%\red{[This section and the next should be merged into a crisp section with the background on DSVerifier, if not included in previous work? 
%Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}
\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}

@@

For convenience, we will use only the notation $G(z)$ to represent the pulse transfer function.
\end{mylemma}

Since $G(z)$ is an approximation of $G(s)$ we denote the error in the approximation for time $t \neq kT$ as $\Delta{G}_P$
\begin{align}
\small
\label{parametric_plant_tf}
\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z).
\end{align}
Note that $\Delta{G}_P$ is undefined and upperbound by a user defined percentage such that $\hat{G}(z)$ corresponds to the polynomial set of possible values of $G(z, T): \forall T \in \mathbb{R}$

Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented using a Fixed Point Finite Word Length with integer size $I$ and fractional size $F$. We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ domain, 
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$,
\begin{align}
\small
\label{FWL_tf}
&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \\
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
\end{align}

\vspace{1 mm} 
\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by the rounding off effect. We may encompass all the uncertainty as $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$. Since this value is nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is denoted by $\mathfrak{G}(z)$.

@@

%\red{[The following description can be made shorter, crisper?]}

The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

%In Step $1$, the user provides inputs $G(z)$ and $\Delta{G}(z)$
%%$\%$ ({\it i.e.}, $\Delta{G}(z)$ as a percentage of $G(z)$)
%, which contain the plant model and the
%interval, respectively.  In Step $2$, a digital controller must be designed
%with any preferred method, where $C(z)$ is obtained.  The controller
%numerical representation and realization form are chosen in Steps $3$ and
%$4$, respectively.  In Step $5$, the user finally configures the
%verification parameters ({\it e.g.}, verification time, properties, and BMC
%tool).  After that, DSVerifier verification engine performs an (automatic)
%verification of the desired property $\phi$ ({\it i.e.}, stability).  The
%user steps described in Steps $1$--$5$ result in an ANSI-C code that should
%be used as an input for DSVerifier.

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$, provided
in an ANSI-C code input file (Steps 1-5),
DSVerifier constructs a non-deterministic model to represent the plant family
$\mathfrak{G}(z)$ (Step A), and a transfer function $f$ [eq. \ref{FWL_tf}]
(step B) to calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$
of the controller (step C).
Finally DSVerifier builds an intermediate ANSI-C code for the digital system
implementation, which is used as input for the model-checker (Step D).

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it i.e.} stability)
is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
If any property violation is found, DSVerifier reports a
counterexample, which contains system inputs or parametric deviations
$\Delta{G}$ that lead the system to a failure.  A successful verification
result is reported if the system is safe with respect to $\phi$.  In
particular, the stability verification is complete and sound, since it does
not depend on system inputs and outputs.
In the case of stability, the specification $\phi$ consists in a number of assumptions
on the polynomial coefficients following Jury's Criteria, as well as the restrictions
set in the representation of these coefficients by the function $f$ [eq. \ref{FWL_tf}].

%In Step A, DSVerifier constructs a non-deterministic model to represent the
%plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
%provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
%Step B using implementation details provided from Steps $2$ and $3$, and
%then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
%intermediate ANSI-C code for the digital system implementation, which is
%used as input for the model-checker, as pointed in Step D.

%This intermediate ANSI-C code model has three main modules: digital
%controller code to be embedded into the microprocessor; plant model code,
%which simulates the plant model dynamics considering uncertainties; and
%``assert'' and ``assume'' statements, which control the verification flow. 
%For the digital controller code, transfer functions coefficients are
%quantized and deterministic, and all operations use fixed-point arithmetic. 
%\textcolor{red}{In the plant model code, transfer function coefficients are
%not quantized, but represented with maximum precision based on float
%data-type variables}; they are treated as non-deterministic variables to
%support model uncertainties.  The directive ``assume'' bounds
%non-deterministic variables, {\it i.e.}, inputs and plant uncertain
%coefficients.
%
%The translation of ANSI-C code into SAT/SMT formulae
%is done by a back-end model-checking tool ({\it e.g.},
%CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).  Here, DSVerifier
%symbolically checks a given property $\phi$ with respect to closed-loop
%systems, which are composed by $f(c_i)$ and every $G$ in $\mathfrak{G}$. 
%If any property violation is found, then DSVerifier reports a
%counterexample, which contains system inputs or parametric deviations
%$\Delta{G}$ that lead the system to a failure.  A successful verification
%result is reported if the system is safe with respect to $\phi$.  In
%particular, the stability verification is complete and sound, since it does
%not depend on system outputs and inputs.

@@

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
    \node[draw=none] (r) {r};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde u(z)$};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu2$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(s)}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$u(s)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (y) {y};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$. \red{[Right: so under this assumption, we really only focus on the quantisation effects introduced by the ADC, correct? Let us not mix up the role and the influence of the two blocks.]}
%
\end{myassumption}

@@
